log

### 2020-04-13 simulation_study/README.Rmd
test ini file
Upgrade hyperparameter optimization plots \n add bar plots for discrete hyperparameters

```{r include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
knitr::opts_chunk$set(echo = FALSE)
```

```{r eval = FALSE}
# 
source("R/00_condition_grid.R")
source("R/01_hyperparameter_sets.R")
```

@@

```{r}
conditiongrid <- readRDS("00_conditiongrid.RDS")

conditiongrid %>%
  kable(format = "markdown")
```

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")

```

@@

Optimization run on Cartesius
```{bash, eval = FALSE}
# BCTW

# RCTW

# SCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402

# LCTW

# NCTW
```

@@

```{bash, eval = FALSE}
# BCTW
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ace -r 23 # 7772446
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d nudging -r 23 # 7772450
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ptsd -r 23 # 7772452
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d software -r 23 # 7772454
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d wilson -r 23 # 7772456
# extract all trials.pkl files 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ace/trials.pkl ~/hyperopt/trials/BCTW_ace.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/nudging/trials.pkl ~/hyperopt/trials/BCTW_nudging.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ptsd/trials.pkl ~/hyperopt/trials/BCTW_ptsd.pkl
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/software/trials.pkl ~/hyperopt/trials/BCTW_software.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/wilson/trials.pkl ~/hyperopt/trials/BCTW_wilson.pkl 
# create config files
asreview create-config trials/BCTW_ace.pkl -o config/BCTW_ace.ini
asreview create-config trials/BCTW_nudging.pkl -o config/BCTW_nudging.ini
asreview create-config trials/BCTW_ptsd.pkl -o config/BCTW_ptsd.ini
asreview create-config trials/BCTW_software.pkl -o config/BCTW_software.ini
asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini

# RCTW

# SCTW

# LCTW

# NCTW

```

@@

```{r}
lubridate::date("2020-03-19")

#todo <- check(todo, "BCTW", "one", datasets)
```

@@

```{bash, eval = FALSE}
# run simulations within cartesius
./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23

./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23

./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23

./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23

./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
```

### extract simulation results nb 
```{bash, eval = FALSE}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output

scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
```

@@

Sent hyperparameters for optimization
```{bash, eval = FALSE}
# SCTW
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d nudging -r 23 # 7805983
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ptsd -r 23 # 7805984
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d software -r 23 # 7805985
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986

# LCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987

# RCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989

# NCTW does not work well with tfidf, save for second round with doc2vec: 
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021

```

@@

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157

# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
```

@@

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
# error 
# accidentally got killed while downgrading tensorflow at the same time. 
# run again, 7815147

# NCDW for remaining datasets

```

@@

Optimize BCTW model 6 datasets (for paper)
```{bash, eval = FALSE}
./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
# create config file (BMTW (M=mixed)) 
asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
# move config to device
scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/

# run simulations (on own device)

# see script

```

@@

```{r}
lubridate::date("2020-03-27")
# todo <- busy(todo, "SCTW", "one", datasets[2:5])

```

@@

```{r}
# save the to-do grid in markdown style
todo[todo==0] <- emo::ji("white square button")
todo %>% kable(format = "markdown")

saveRDS(todo %>% kable(format = "markdown"), 
        file = "02_todo_hp.RDS")
```

@@

```
************  ace.csv  ************

Number of papers:            2235
Number of inclusions:        41 (1.83%)
Number of exclusions:        2194 (98.17%)
Number of unlabeled:         0 (0.00%)
Average title length:        123
Average abstract length:     1623
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  nudging.csv  ************

Number of papers:            1847
Number of inclusions:        100 (5.41%)
Number of exclusions:        1747 (94.59%)
Number of unlabeled:         0 (0.00%)
Average title length:        109
Average abstract length:     1831
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  ptsd.csv  ************

Number of papers:            5031
Number of inclusions:        38 (0.76%)
Number of exclusions:        4993 (99.24%)
Number of unlabeled:         0 (0.00%)
Average title length:        104
Average abstract length:     1537
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  software.csv  ************

Number of papers:            8896
Number of inclusions:        104 (1.17%)
Number of exclusions:        8792 (98.83%)
Number of unlabeled:         0 (0.00%)
Average title length:        81
Average abstract length:     896
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)

************  wilson.csv  ************

Number of papers:            2333
Number of inclusions:        23 (0.99%)
Number of exclusions:        2310 (99.01%)
Number of unlabeled:         0 (0.00%)
Average title length:        83
Average abstract length:     1325
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
```

>>>>

```{r, include = FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
source("R/functions.R")
knitr::opts_chunk$set(echo = FALSE)
```

```{r, eval = FALSE}
# 
source("R/00_condition_grid.R")
source("R/01_hyperparameter_sets.R")
```

@@

```{r}
conditiongrid <- readRDS("R/00_conditiongrid.RDS")
conditiongrid %>%
  kable(format = "markdown")
```

@@

# Stage 1 - Classifiers 
Comparing five different classifiers
```{r}
emptytodo <- readRDS("R/01_hyperparameter_sets.RDS")
todo <- emptytodo
```

@@

Optimization run on Cartesius
```{bash, eval = FALSE}
# BCTW
# RCTW
# SCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ace -r 23 # job id 7768402
# LCTW
# NCTW
```

@@

```{bash, eval = FALSE}
# BCTW
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ace -r 23 # 7772446
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d nudging -r 23 # 7772450
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d ptsd -r 23 # 7772452
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d software -r 23 # 7772454
./cart_hyper_run.py hyper-active -t 03:00:00 -m nb -b double -e tfidf -q max -d wilson -r 23 # 7772456
# extract all trials.pkl files 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ace/trials.pkl ~/hyperopt/trials/BCTW_ace.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/nudging/trials.pkl ~/hyperopt/trials/BCTW_nudging.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/ptsd/trials.pkl ~/hyperopt/trials/BCTW_ptsd.pkl
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/software/trials.pkl ~/hyperopt/trials/BCTW_software.pkl 
scp gerbrich@cartesius.surfsara.nl:asreview/output/active/nb_max_double_tfidf/wilson/trials.pkl ~/hyperopt/trials/BCTW_wilson.pkl 
# create config files
asreview create-config trials/BCTW_ace.pkl -o config/BCTW_ace.ini
asreview create-config trials/BCTW_nudging.pkl -o config/BCTW_nudging.ini
asreview create-config trials/BCTW_ptsd.pkl -o config/BCTW_ptsd.ini
asreview create-config trials/BCTW_software.pkl -o config/BCTW_software.ini
asreview create-config trials/BCTW_wilson.pkl -o config/BCTW_wilson.ini
# RCTW
# SCTW 
# LCTW
# NCTW
```

@@

```{r}
lubridate::date("2020-03-19")
#todo <- check(todo, "BCTW", "one", datasets)
```

@@

```{bash, eval = FALSE}
# run simulations within cartesius
./cart_simulate.py data/ace.csv --config_file config/BCTW_ace.ini --state_file "simoutput/bctw/ace/BCTW_ace.h5" -r 23 
./cart_simulate.py data/nudging.csv --config_file config/BCTW_nudging.ini --state_file "simoutput/bctw/nudging/BCTW_nudging.h5" -r 23 
./cart_simulate.py data/ptsd.csv --config_file config/BCTW_ptsd.ini --state_file "simoutput/bctw/ptsd/BCTW_ptsd.h5" -r 23 
./cart_simulate.py data/software.csv --config_file config/BCTW_software.ini --state_file "simoutput/bctw/software/BCTW_software.h5" -r 23 
./cart_simulate.py data/wilson.csv --config_file config/BCTW_wilson.ini --state_file "simoutput/bctw/wilson/BCTW_wilson.h5" -r 23 
```

### extract simulation results nb 
```{bash, eval = FALSE}
# transfer files to device 
scp -r gerbrich@cartesius.surfsara.nl:asreview/simoutput /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/simulation_output
scp -r /Users/gerbrich/Documents/MSBBSS/asreviewthesis/asreview-thesis/hyperopt/config/one gerbrich@cartesius.surfsara.nl:asreview/simulations/automated-systematic-review-simulations/scripts/config
```

@@

Sent hyperparameters for optimization
```{bash, eval = FALSE}
# SCTW
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d nudging -r 23 # 7805983
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d ptsd -r 23 # 7805984
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d software -r 23 # 7805985
./cart_hyper_run.py hyper-active -t 12:00:00 -m svm -b double -e tfidf -q max -d wilson -r 23 # 7805986
# LCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m lr -b double -e tfidf -q max -d ace -r 23 # 7805987
# RCTW 
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7805989
# NCTW does not work well with tfidf, save for second round with doc2vec: 
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7806021
```

@@

```{bash, eval = FALSE}
# LCTW 
# made a mistake in command, "logistic" instead of "lr", run again 
./cart_hyper_run.py hyper-active -t 03:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7813556
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m logistic -b double -e tfidf -q max -d ace -r 23 # 7815137
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d nudging -r 23 # 7815154
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d ptsd -r 23 # 7815155
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d software -r 23 # 7815156
./cart_hyper_run.py hyper-active -t 12:00:00 -m logistic -b double -e tfidf -q max -d wilson -r 23 # 7815157
# RCTW, fixed a parameter bug in simulation package. 
./cart_hyper_run.py hyper-active -t 03:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7813592
# evaluated run, now other datasets
./cart_hyper_run.py hyper-active -t 09:00:00 -m rf -b double -e tfidf -q max -d ace -r 23 # 7815139
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d nudging -r 23 # 7815158
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d ptsd -r 23 # 7815159
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d software -r 23 # 7815160
./cart_hyper_run.py hyper-active -t 12:00:00 -m rf -b double -e tfidf -q max -d wilson -r 23 # 7815162
```

@@

NCDW - loss still going down, sent in for another 12 hours. 
```{bash, eval = FALSE}
# NCDW
./cart_hyper_run.py hyper-active -t 12:00:00 -m nn-2-layer -b double -e doc2vec -q max -d ace -r 23 # 7811926
# error 
# accidentally got killed while downgrading tensorflow at the same time. 
# run again, 7815147
# NCDW for remaining datasets 
```

@@

Optimize BCTW model 6 datasets (for paper)
```{bash, eval = FALSE}
./cart_hyper_run.py hyper-active -t 5 -b triple -r 23 # 7815097
./cart_hyper_run.py hyper-active -t 12:00:00 -b triple -r 23 # 7815102
# create config file (BMTW (M=mixed)) 
asreview create-config output/active/nb_max_random_triple_tfidf/ptsd_virus_ace_software_wilson_nudging/trials.pkl -o config/BMTW_all.ini
# move config to device
scp gerbrich@cartesius.surfsara.nl:asreview/config/BMTW_all.ini ~/
# run simulations (on own device)
# see script
```

@@

```{r}
lubridate::date("2020-03-27")
# todo <- busy(todo, "SCTW", "one", datasets[2:5])
```

@@

```{r}
# save the to-do grid in markdown style
todo[todo==0] <- emo::ji("white square button")
todo %>% kable(format = "markdown")
saveRDS(todo %>% kable(format = "markdown"), 
        file = "02_todo_hp.RDS")
```

@@

```
************  ace.csv  ************
Number of papers:            2235
Number of inclusions:        41 (1.83%)
Number of exclusions:        2194 (98.17%)
Number of unlabeled:         0 (0.00%)
Average title length:        123
Average abstract length:     1623
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  nudging.csv  ************
Number of papers:            1847
Number of inclusions:        100 (5.41%)
Number of exclusions:        1747 (94.59%)
Number of unlabeled:         0 (0.00%)
Average title length:        109
Average abstract length:     1831
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  ptsd.csv  ************
Number of papers:            5031
Number of inclusions:        38 (0.76%)
Number of exclusions:        4993 (99.24%)
Number of unlabeled:         0 (0.00%)
Average title length:        104
Average abstract length:     1537
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  software.csv  ************
Number of papers:            8896
Number of inclusions:        104 (1.17%)
Number of exclusions:        8792 (98.83%)
Number of unlabeled:         0 (0.00%)
Average title length:        81
Average abstract length:     896
Number of missing titles:    0 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
************  wilson.csv  ************
Number of papers:            2333
Number of inclusions:        23 (0.99%)
Number of exclusions:        2310 (99.01%)
Number of unlabeled:         0 (0.00%)
Average title length:        83
Average abstract length:     1325
Number of missing titles:    1 (of which 0 included)
Number of missing abstracts: 0 (of which 0 included)
```
